Probabilistic Forecast Reconciliation

### 2018-11-10 Presentation/ProbForeRec.tex
added more pictures to presentation

\documentclass[handout]{beamer}
\usetheme{Warsaw}
\usepackage{amsmath,amsthm, bm, tikz,qtree}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage[greek,english]{babel}

@@

@@

@@

  \item Forecasts do not respect aggregation structure ({\bf Incoherent})
  \item Outcome {\em does} respect aggregation  structure ({\bf Coherent})

@@

  \begin{frame}{What we do NOT do}
  	\item All information is contained in the most disaggregate series.
  	\item In principle using the correct multivariate model for the most disaggregate series and aggregating them should work.
  	\item Disaggregate series are: 
  		\item Very noisy
  		\item High-dimensional
  		\item Prone to model misspecification

@@

    	\item Let $n$ be the number of series, $\bm{y}$ be an n-vector of all series.
    	\only<2>{\item Let {\color{blue}$m$} be the number of bottom level series and {\color{blue}$\bm{b}$} be an {\color{blue}$m$}-vector of the bottom level series.}

@@

  	\item Cast the problem as a regression model with base forecasts $\hat{\bm{y}}$ as the ``dependent variable'' and ${\bm S}$ as the ``design matrix''. 

@@

  	\hat{\bm{y}}={\bm{S}}{\bm\beta}+{\bm e}

@@

  	\tilde{\bm{y}}={\bm S}({\bm S}'{\bm S})^{-1}{\bm S}'{\hat{\bm{y}}}

@@

  \tilde{\bm{y}}={\bm S}({\bm S}'{\bm W}^{-1}{\bm S})^{-1}{\bm S}'{\bm W}^{-1}{\hat{\bm{y}}}

@@

  \item Consider the covariance matrix of ${\bm y}-\hat{\bm{y}}$.

@@

@@

  \begin{frame}{Animation}
  content...

@@

  	Let $g:\mathbb{R}^n\rightarrow\mathbb{R}^m$ be a mapping.  Then 

@@

  	Consider case where the base true predictive distributions are elliptical.

@@

  		There exists a function $\bm{G}$ such that the true predictive distribution can be recovered by linear reconciliation.

@@

  		\item Suppose $\bm{\hat{y}}^{[1]},\ldots,\bm{\hat{y}}^{[J]}$ is a sample from the unreconciled probabilistic forecast.
  		\item Then setting $\tilde{\bm y}^{[j]}=\bm{S}\bm{G}\hat{\bm y}^{[j]}$ produces a sample from the reconciled distribution with respect to $g$.

@@

   		\item We have run lots of simulations

@@

   		    	\item OLS (an orthogonal projection) does poorly.

@@

>>>>

\documentclass{beamer}
\usetheme{Warsaw}
\usepackage{amsmath,amsthm, bm, tikz,qtree}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage[greek,english]{babel}

@@

  	\item Multiple time series $\rightarrow$ some series are aggregates of others.

@@

  	\pause

@@

  \pause
  \item Forecasts do not respect aggregation structure \pause({\bf Incoherent})\pause
  \item Outcome {\em does} respect aggregation  structure \pause ({\bf Coherent})\pause

@@

%  \begin{frame}{What we do NOT do}
%  	\item All information is contained in the most disaggregate series.
%  	\item In principle using the correct multivariate model for the most disaggregate series and aggregating them should work.
%  	\item Disaggregate series are: 
%  		\item Very noisy
%  		\item High-dimensional
%  		\item Prone to model misspecification

@@

    	\item Let $n$ be the number of series, $\bm{y}_t$ be an n-vector of all series.
    	\only<2>{\item Let {\color{blue}$m$} be the number of bottom level series and {\color{blue}$\bm{b}_t$} be an {\color{blue}$m$}-vector of the bottom level series.}

@@

  	\item Cast the problem as a regression model with base forecasts $\hat{\bm{y}}_{T+h}$ as the ``dependent variable'' and ${\bm S}$ as the ``design matrix''. 

@@

  	\hat{\bm{y}}_{T+h}={\bm{S}}{\bm\beta}_{T+h}+{\bm e}_{T+h}

@@

  	\tilde{\bm{y}}_{T+h}={\bm S}({\bm S}'{\bm S})^{-1}{\bm S}'{\hat{\bm{y}}}_{T+h}

@@

  \tilde{\bm{y}}_{T+h}={\bm S}({\bm S}'{\bm W}^{-1}{\bm S})^{-1}{\bm S}'{\bm W}^{-1}{\hat{\bm{y}}}_{T+h}

@@

  \item Consider the covariance matrix of ${\bm y}_{T+h}-\hat{\bm{y}}_{T+h}$.
   \pause

@@

   \bm{W}=\sum\limits_{t=1}^T ({\bm y}_{t}-\hat{\bm{y}}_{t})({\bm y}_{t}-\hat{\bm{y}}_{t})'
  \pause

@@

\begin{frame}{In-Sample errors}
\input{Figs/insample}
\begin{frame}{Most likely direction}
\input{Figs/insampledir}
\input{Figs/oblique_justification1}
\input{Figs/oblique_justification2}

@@

  	Let $g:\mathbb{R}^n\rightarrow\mathbb{R}^m$ be a function.  Then 

@@

  	Consider case where the base and true predictive distributions are elliptical.

@@

  		There exists a matrix $\bm{G}$ such that the true predictive distribution can be recovered by linear reconciliation.

@@

  		\pause
  		\item Suppose $\bm{\hat{y}}_{T+h}^{[1]},\ldots,\bm{\hat{y}}_{T+h}^{[J]}$ is a sample from the unreconciled probabilistic forecast.
  		\pause
  		\item Then setting $\tilde{\bm y}_{T+h}^{[j]}=\bm{S}\bm{G}\hat{\bm y}_{T+h}^{[j]}$ produces a sample from the reconciled distribution with respect to $g$.

@@

   		\item We have run lots of simulations.
   		\pause

@@

   		    	\pause
   		    	\item OLS (an orthogonal projection) does reasonably well.
   		    	\pause

@@

        \pause
        \pause
